TBD

### 2016-10-14 paper.tex
cg

Recall that we mentioned that in general we can only solve Eq.~\eqref{eq:linear_system} with CG if $\bA$ is a square positive-definite Hermitian matrix. Recently,
\citet{Lu2015} showed that the CG method has an even broader applicability, it can be used to solve Eq.~\eqref{eq:linear_system} even if $\bA$ is an Hermitian positive semi-definite
square matrix as long as $\bb$ is in the column range of $\bA$.

@@

Note that if $\bA$ is positive semi-definite its smallest eigenvalue is zero, which implies that Eq.~\eqref{eq:kappa} is not defined. \citet{Lu2015} show that when $\bA$
is a square positive semi-definite Hermitian matrix we do not use the spectral condition number to bound the convergence complexity of CG, but the general spectral condition
number instead. The general spectral condition number is very similar to the spectral condition number, the only difference being that in Eq.~\eqref{eq:kappa} we replace  
$\lambda_{\textrm{min}}$ with $\lambda_{\textrm{min}}^+$, which denotes the smallest positive eigenvalue.

>>>>

Recall that we mentioned that in general we can only solve Eq.~\eqref{eq:linear_system} with CG if $\bA$ is a square positive-definite Hermitian matrix. The CG method actually has an even broader applicability, it can be used to solve Eq.~\eqref{eq:linear_system} even if $\bA$ is an Hermitian positive semi-definite
square matrix as long as $\bb$ is in the column range of $\bA$ \citep{Lu2015}.

@@

Note that if $\bA$ is positive semi-definite its smallest eigenvalue is zero, which implies that Eq.~\eqref{eq:kappa} is not defined. \citet{Lu2015} show that when $\bA$
is a square positive semi-definite Hermitian matrix we do not use the spectral condition number to bound the convergence complexity of CG, but the general spectral condition
number instead. The general spectral condition number is very similar to the spectral condition number; the only difference being that in Eq.~\eqref{eq:kappa} we replace  
$\lambda_{\textrm{min}}$ with $\lambda_{\textrm{min}}^+$, which denotes the smallest positive eigenvalue.
